### 2015-05-14 corral.tex
fixes

We have implemented two different levels of context-switch instrumentation granularity:

\yieldcoarse instruments \texttt{yield} statement in a binary fashion: if \whoop
finds that a pair of entry points cannot race, then it will only instrument
context-switches in synchronization points (i.e.\ locks and unlocks) of this pair; else if \whoop finds
that a pair of entry points can race, then it will instrument context-switches
in all visible operations of this pair.

\yieldmr is a finer-grained instrumentation: \whoop instruments context-switches
in all synchronization points, but only instruments context-switches in memory
regions that can potentially race (regardless if a pair has not been fully
verified as race-free). In our experiments (see \S\ref{evaluation}),
\yieldmr performs significantly faster than \yieldcoarse.

>>>>

We have implemented two different \texttt{yield} instrumentations in \whoop: \yieldcoarse and \yieldmr.
%
\yieldcoarse instruments \texttt{yield} statements in a binary fashion: if \whoop finds that a pair of entry points cannot race, then it will instrument a \texttt{yield} only after each lock and unlock statement of this pair; else if \whoop finds that a pair of entry points might race, then it will instrument context-switches after all visible operations of this pair.
%
\yieldmr performs a finer-grained instrumentation: it instruments context-switches only after each memory region that can potentially race (regardless if a pair has not been fully verified as race-free) and after each lock and unlock. In our experiments (see \S\ref{evaluation}), \yieldmr significantly outperforms \yieldcoarse.
